---
title: "Measles Mitigation, Tracking Childhood Immunization Across Nations"
subtitle: "The top performers and worrying trends"
author: "Cormac McNally"
date: "04/23/2024"
format:
  html: 
   theme: quartz
   toc: true
execute: 
  echo: false
  warning: false
  message: false
---


Vaccinating children against measles is a fundamental pillar of public health initiaties worldwide.

Measles is a highly contagious viral disease that poses significant risks to public health. Vaccines play a crucial role in preventing outbreaks, safeguarding vulnerable populations, abd contributing to global health security. Measles was once considered nearly eradicated in many parts of the world, but has seen a resurgence in recent years due to gaps in vaccination coverage. This resurgence serves as a stark reminder of the importance of maintaining high vaccination uptake worldwide.





```{r}
#| label: setup
#| include: false

# libraries
library(tidyverse)

#data
data <- read_csv("unicef_indicator_2 (3).csv")

# transformations
# List of countries for time series analysis
countries <- c("United States", "Russia", "Germany", "China", "Japan", "India", "France", "United Kingdom", "Brazil")

# Filter the data for the countries of interest
data_filtered <- data[data$country %in% countries,]
```
## World Vaccination uptake in 2022
```{r}
# World map

data_2022 <- data %>%
  filter(time_period ==2022)
map_world <- map_data("world")
map_data_join <- full_join(data_2022, map_world, by = c("country" = "region"))
ggplot(map_data_join) +
  aes(x = long, y = lat, group = group, fill = obs_value) +
  geom_polygon() +
  labs(title = "World vaccination uptake in 2022")

```

Below, is a time series chart of our Global Superpowers. Most notably, Japan had a late uptake in nationwide vaccine rollout and has fought immense skepticism among the general population.
Brazil has experienced a relatively inconsistent vaccine uptake, and failes to deliver in an effective nationwide vaccination programme.
```{r}
# Time series chart for all selected countries
p <- ggplot(data_filtered, aes(x=time_period, y=obs_value, color=country))+
  geom_line()+  
  labs(title = "Time Series Chart for Vaccinations among Global Superpowers",
  x="Year",
  y="% Vaccinated") +
  theme(legend.position="bottom", legend.box = "horizontal") +  
  scale_color_discrete(name = "Country") 
print(p)
```
China has consistently lead the fight against measles, topping every nation among the superpowers across the years. Japan has also made significant strides throughout the past few years.

## Worrying trends from North Korea

```{r}
# Bar chart for "Korea, Democratic People's Republic of"
data_korea <- data[data$country == "Korea, Democratic People's Republic of",]
p1 <- ggplot(data_korea, aes(x=time_period, y=obs_value)) +
  geom_bar(stat="identity") +
  labs(title = "Bar Chart for Democratic People's Republic of North Korea",
  y="% Vaccinated",
  x="Year")
print(p1)
```
Democratic People's Republic of North Korea is the lowest performing country for vaccinations at 0%. Often shrouded in secrecy and controversy, it has faced numerous challenges, including healthcare issues. In recent years the decline in vaccinations, particularly for diseases like measles, has emerged as a significant concern within the international community.

Political tensions and isolationist policies have impeded international efforts to provide assistance and support for North Korea's healthcare infrastructure. Sanctions imposed on the regime have further exacerbated these challenges, as hindering access to crucial medical resources and impeding collaboration with international health organisations.

Measles is a highly contagious virus which can spread rapidly in communities with low vaccination rates, posing a significant threat to public health, particularly among children who are most vulnerable to its effects.

```{r}
# Filtered countries for the scatterplot
data_filtered <- data[data$country %in% countries,]

# Scatterplot
p2 <- ggplot(data_filtered, aes(x=time_period, y=obs_value, color=country)) +
  geom_point() +  
  geom_smooth(method=lm , color="red", se=FALSE) +  
  labs(title = "Scatterplot of vaccinations over the years",
  x="Year",
  y="% Vaccinated")+
  theme(legend.position="bottom", legend.box = "horizontal")+  
  scale_color_discrete(name = "Country")
print(p2)
```
Germany, renowned for its strong healthcare system, implemented comprehensive vaccination campaigns targeting children across the country. In Hungary, a commitment to childhood immunization remained steadfast. The government prioritized vaccine accessibility and education, and ensuring that parents understood the importance of vaccinating their children against measles.

## Conclusion
In today's interconnected world, disease knows no boundaries. A measles outbreak in one corner of the globe can quickly escalate into a global health crisis. Measles is now on the rise once again, and the WHO plays a pivotal role in mitigating this global threat to humanity.




